Untitled

### 2017-07-23 PaperCode.Rmd
Average local prices
Wrote a script to calculate the price of a LAD relative to the local population of LADs... it doesn't improve any models

@@

#gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
CurrentLADS <- ls(pattern = "DATA") %>%
  map_chr(~{df<- get(.x)
  df$LAD11CD[which.max(table(df$LAD11CD) %>% as.matrix)] }
)

@@

BootStrapRES$CoLLON %>% PlotClassDiff()
BootStrapRESExO$CoLLON %>% PlotClassDiff()
BootStrapRESA$CoLLON %>% PlotClassDiff()
BootStrapRESB$CoLLON %>% PlotClassDiff()

@@

#test CoL after adding in filtering for other LADs
testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, PropertyTypes = c("D", "S", "T", "F"))

testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A", PropertyTypes = c("D", "S", "T", "F"))
testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B", PropertyTypes = c("D", "S", "T", "F"))

all_equal(Boottest$CoLLON, testCol)

all_equal(Boottest$CoLLON, BootStrapRES$CoLLON)

testCol %>% PlotClassDiff()

testColA %>% 
  group_by(class) %>%
  summarise_all(funs(mean(., na.rm = TRUE)))

@@

test <- Combine1 %>% 
  left_join(ABratio4)

test %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()

test %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()

test %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()

@@

Combine1[Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5,]
Combine2[Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5,]
Combine3[Combine3$Ttest.p.value>0.5 & Combine3$maxPerc>5,]

@@

Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

@@

test <- Combine1 %>% filter(Ttest.p.value>0.05)
```

>>>>

#Overall price data 
```{r}
#Other property is massively more valuable on average than the rest of the property types
#mean value is 10 Million as such it has to be excluded
prices %>% group_by(X5) %>% 
  mutate(X2 = as.numeric(X2)) %>%
  summarise(count = n(),
            Value = sum(X2, na.rm =T),
            mean = mean(X2, na.rm = T)) %>%
mutate(countperc = (count/sum(count)),
       ValuePerc = Value/sum(Value))

#Looking at A and B property we can see that B properties are more expensive than A type
prices %>% group_by(X15) %>% 
  mutate(X2 = as.numeric(X2)) %>%
  summarise(count = n(),
            Value = sum(X2, na.rm =T),
            mean = mean(X2, na.rm = T)) %>%
mutate(countperc = (count/sum(count)),
       ValuePerc = Value/sum(Value))

#Other only appears in the B type sales never in A type
prices %>% 
  mutate(X2 = as.numeric(X2)) %>%
    group_by(X15, X5) %>% 
  summarise(count = n(),
            Value = sum(X2, na.rm =T),
            mean = mean(X2, na.rm = T)) %>%
  ungroup %>%
mutate(countperc = (count/sum(count)),
       ValuePerc = Value/sum(Value))  
```

@@

#gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
CurrentLADS <- ls(pattern = "DATA") %>%
  map_chr(~{df<- get(.x)
  df <- df %>%
  group_by(LAD11CD) %>%
  summarise(count = n())
df$LAD11CD[which.max(df$count)]}
)

@@

BootStrapRES$CoLLON %>% PlotClassDiff()
BootStrapRESExO$CoLLON %>% PlotClassDiff()
BootStrapRESExOA$CoLLON %>% PlotClassDiff()
BootStrapRESExOB$CoLLON %>% PlotClassDiff()

@@

@@

CombineAB <- Combine1ExO %>% 
  left_join(ABratio4, by = "LAD11CD")

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()

#Inlcuding deprivation
```{r}
setwd(file.path(basewd, "Deprivation"))
list.files()
LADDep<-read_excel("File_10_ID2015_Local_Authority_District_Summaries.xlsx", sheet = 2) %>%
  setNames(make.names(names(.)) %>% gsub("IMD...", "",.) %>% trimws ) %>%
  rename(LAD11CD = Local.Authority.District.code..2013.)

LSOADomDep<-read_excel("File_2_ID_2015_Domains_of_deprivation.xlsx" , sheet = 2) %>%
  setNames(make.names(names(.))) %>%
  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
  rename(LAD11CD = Local.Authority.District.code..2013.)

LSOADep<-read_excel("File_1_ID_2015_Index_of_Multiple_Deprivation.xlsx", sheet = 2) %>%
  setNames(make.names(names(.))) %>%
  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
  rename(LAD11CD = Local.Authority.District.code..2013.,
         LSOA_CODE = LSOA.code..2011.)

CombineAB <- CombineAB %>% left_join(LADDep, by = "LAD11CD")

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, color =Rank.of.extent<100)) + geom_jitter()

#Look Kings Lynn and harrogate as they are strange results

KingsLynnDep <- KingsLynnDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>% 
  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))

HarrogateDep <- HarrogateDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>%
  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))

#creating the empty deprivation extent
maxLSOA <- max(LSOADep$Rank..where.1.is.most.deprived.)

ExtentWeight <- LSOADep%>%
  mutate(percentile = (Rank..where.1.is.most.deprived./maxLSOA),
         perc2 = percentile-0.11,
         weight = ifelse(percentile<.11|percentile>.3,0, 0.95 - (0.95/.20)*perc2 ),
         weight = ifelse(percentile<0.11, 1, weight)) %>%
  select(LSOA_CODE, weight)

test <- KingsLynnDep %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

test <- BromleyLONDATA %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

sum(test$WeightedLUP, na.rm = TRUE)

LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
df <- get(.x)
test <- df %>% 
  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))

sum(test$WeightedLUP, na.rm = TRUE)
})

Combine1ExO2 <- CombineAB%>%
  mutate(LUPdepExt)

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_point()

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_point()

LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(meandiff = price-mean(price),
         pricepercent = percent_rank(price))

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
  mutate(outcome = LUPdepExt>Extent)

test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_point()

svm.model <- svm(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
#why do the two rforest models have such different results
rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)

confusionMatrix(predict(svm.model, test, type = class),as.factor(test$absdiff>0))

confusionMatrix( predict(rpart.model, test, type = "class"),as.factor(test$absdiff>0))

library(e1071)
 library(rpart)
 data(Glass, package="mlbench")
 ## split data into a train and test set
 index <- 1:nrow(Glass)
 testindex <- sample(index, trunc(length(index)/3))
 testset <- Glass[testindex,]
 trainset <- Glass[-testindex,]

svm.model <- svm(Type ~ ., data = trainset, cost = 100, gamma = 1)
svm.pred <- predict(svm.model, testset[,-10])

rpart.model <- rpart(Type ~ ., data = trainset)
rpart.pred <- predict(rpart.model, testset[,-10], type = "class")

confusionMatrix( rpart.pred, testset$Type)
confusionMatrix( svm.pred, testset$Type)
```

@@

Combine1ExO[Combine1ExO$Ttest.p.value>0.5 & Combine1ExO$maxPerc>5,]
Combine2ExO[Combine2ExO$Ttest.p.value>0.5 & Combine2ExO$maxPerc>5,]
Combine3ExO[Combine3ExO$Ttest.p.value>0.5 & Combine3ExO$maxPerc>5,]

@@

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

@@

```{r}
test <- Combine1 %>% filter(Ttest.p.value>0.05)
```
